\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation

### 2018-05-06 ccs/conclude.tex
changes, comments

>>>>

\section{Conclusion and Future Work}
\label{sec:conclude}
We presented \tool, the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to, or better than the custom, specialized
protocols from previous works.
The \mpc backed we use provides security against semi-honest or passive adversaries.
%our compiler is oblivious to the ``type of adversary'' for the underlying \mpc backend.
Given a \mpc backend secure against malicious or active adversaries, Theorem \ref{theorem:security} 
can be extended to obtain a framework with malicious security. Furthermore,  
partitioning can be modified to provide malicious security by {\it signing} the shares of the intermediate states. However, we are not aware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits.

\dg{Add other future work such as language enhancement to support public inputs, declassification of intermediate values, secret array indices and support of ORAM. But since current focus was ML applications, didn't require these as such. Also, crypto backends would keep improving and although our ideas extend to works such as Gazelle, we leave integrating it as a backend in \tool as future work.}

### 2018-05-06 ccs/eval.tex
starting ccs repo
changes, comments

\vspace{-0.1in}
\section{Evaluation}
\label{sec:eval}
We evaluate \tool on a variety of problems that can fall under the umbrella of {\it secure prediction}, where one
party (the server) has a machine learning model, and the other party
(the client) has an input. The goal is to compute the output of the
model on client's input, with the guarantee that the server
learns nothing about the input, and the client learns nothing
about the model beyond what is revealed from the output.

@@

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. Where we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (as the code for works such as Bost et al. \cite{shafindss} and \minion~\cite{minionn} are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning and we set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

@@

%dataset | time | comm | timeL | timeW | comm
%Our decision tree numbers in Table~\ref{tab:dt} further validate
%this claim. 
%We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
%describe specialized protocols for trees and forests (that perform
%better than~\cite{shafindss}).
%Similar to Bost et al.~\cite{shafindss}, they also remarks that these
%computations are infeasible with Yao-based 2PC.
%Again, we observe that
%the performance of \tool generated generic 2PC
%code is competitive with specialized protocols. 
The results for Na\"{i}ve Bayes are
in Table~\ref{tab:nb}. As before, $n$ denotes the number of classes and $F$ is the number of features.
%Although, there are no multiplications in these benchmarks, these do
%have a significant number of comparisons (due to array look-ups using
%secret indices) that
%result in many boolean-and gates. %(13k/750k denote 13000/75000). 
As before, we compare with Bost et al.~\cite{shafindss} and observe that \tool generated code
has better performance, despite using a generic 2PC,
as opposed to custom designed protocols developed by Bost et
al. Moreover, they remark that in their setup, generic Yao-based 2PC
did not scale to the smallest of their Na\"{i}ve Bayes classifiers, so
they had to scale down the prediction task, and even then Yao-based \mpc
was 500x slower. Whereas, we show that by using a
cryptographic-cost aware compiler, we can scale generic 2PC to real
prediction tasks, and get performance competitive to or better than the
specialized protocols. Table~\ref{tab:dt} 
compares against the more recent work of~\cite{wu}
on decision trees and further validates this claim.
\vspace{-0.2in}
\paragraph{Deep neural nets.}
We evaluate \tool on the DNNs described in SecureML~\cite{secureml},
Cryptonets~\cite{cryptonets}, and the CNN from \minion~\cite{minionn}. For
comparison, we consider their implementations from
\minion~\cite{minionn}, which outperforms their previous
implementations. Table~\ref{tab:nn} shows the
results\footnote{\minion does not report the network round-trip time nor the bit-length of their inputs (we use $32$-bit inputs).}.
We note that for each of these DNNs, \minion provides a
specialized protocol, while \tool uses a generic 2PC protocol
(auto) generated from high-level code.

@@

In Table~\ref{tab:nn}, 
the column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both the LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that while the \minion implementation is based on the ABY framework, it does not use the framework ``off-the-shelf'' and provide tailor-made optimizations for their applications. By contrast, \tool focuses on generic
2PC, exploiting ABY's performant implementation. Optimizations such as those found in \minion are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in \sectionref{pipeeval}.
\vspace{-0.18in}
\paragraph{State-of-the-art classifiers.}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of
digits 0 to 9.
The first model that the tutorial describes is a softmax regression
that provides an accuracy of 92\%. The classifier evaluates
$ \mathsf{argmax}\ W\matmul x+b$.
Here, $x$ is a 784 length vector obtained from the input image,
 $W$ is a $10\times 784$ matrix, and  $b$ is a $10$ length
vector.
We implement this classifier in \tool and present the results in the
first row of Table~\ref{tab:tf}. 
%We note that a pure boolean circuit for this simple functionality does not fit in the memory of our machines and cannot be evaluated using garbled circuits.

@@

>>>>

%\vspace{-0.2in}
\section{Evaluation}
\label{sec:eval}
We evaluate \tool on a variety of problems that can fall under the umbrella of {\it secure prediction}, where one
party (the server) has a machine learning model, and the other party
(the client) has an input. The goal is to compute the output of the
model on client's input, with the guarantee that the server
learns nothing about the input, and the client learns nothing
about the model beyond what is revealed from the output.

@@

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. When we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (as the code for works such as Bost et al. \cite{shafindss} and \minion~\cite{minionn} are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning and we set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

@@

%dataset | time | comm | timeL | timeW | comm
%Our decision tree numbers in Table~\ref{tab:dt} further validate
%this claim. 
%We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
%describe specialized protocols for trees and forests (that perform
%better than~\cite{shafindss}).
%Similar to Bost et al.~\cite{shafindss}, they also remarks that these
%computations are infeasible with Yao-based 2PC.
%Again, we observe that
%the performance of \tool generated generic 2PC
%code is competitive with specialized protocols. 
The results for Na\"{i}ve Bayes are
in Table~\ref{tab:nb}. As before, $n$ denotes the number of classes and $F$ is the number of features.
%Although, there are no multiplications in these benchmarks, these do
%have a significant number of comparisons (due to array look-ups using
%secret indices) that
%result in many boolean-and gates. %(13k/750k denote 13000/75000). 
As before, we compare with Bost et al.~\cite{shafindss} and observe that \tool generated code
has better performance, despite using a generic 2PC,
as opposed to custom designed protocols developed by Bost et
al. Moreover, they remark that in their setup, generic Yao-based 2PC
did not scale to the smallest of their Na\"{i}ve Bayes classifiers, so
they had to scale down the prediction task, and even then Yao-based \mpc
was 500x slower. Whereas, we show that by using a
cryptographic-cost aware compiler, we can scale generic 2PC to real
prediction tasks, and get performance competitive to or better than the
specialized protocols. Table~\ref{tab:dt} 
compares against the more recent work of~\cite{wu}
on decision trees and further validates this claim.

\paragraph{Deep neural nets.}
We evaluate \tool on the DNNs described in SecureML~\cite{secureml},
Cryptonets~\cite{cryptonets}, and the CNN from \minion~\cite{minionn}. For
comparison, we consider their implementations from
\minion~\cite{minionn}, which outperforms their previous
implementations. Table~\ref{tab:nn} shows the
results\footnote{\minion does not report the network round-trip time nor the bit-length of their inputs (we use $32$-bit inputs).}.
We note that for each of these DNNs, \minion provides a
specialized protocol, while \tool uses a generic 2PC protocol
(auto) generated from high-level code.

@@

In Table~\ref{tab:nn}, 
the column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both the LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that while the \minion implementation is based on the ABY framework, it does not use the framework ``off-the-shelf'' and provide tailor-made optimizations for their applications. By contrast, \tool focuses on generic
2PC, exploiting ABY's performant implementation. Optimizations such as those found in \minion are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in \sectionref{pipeeval}.

\paragraph{State-of-the-art classifiers.}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of
digits 0 to 9.
The first model that the tutorial describes is a softmax regression
that provides an accuracy of 92\%. The classifier evaluates
$ \mathsf{argmax}\ W\matmul x+b$.
Here, $x$ is a 784 length vector obtained from the input image,
 $W$ is a $10\times 784$ matrix, and  $b$ is a $10$ length
vector.
We implement this classifier in \tool and present the results in the
first row of Table~\ref{tab:tf}. 
%We note that a pure boolean circuit for this simple functionality does not fit in the memory of our machines and cannot be evaluated using garbled circuits.

@@

\subsection{Subsequent Work}
\TODO{....}

### 2018-05-06 ccs/ex.tex
changes, comments

\vspace{-0.1in}
\section{\tool Overview}
\label{sec:ex}
%$w^Tx>0$, mnist logistic regression
%% \divya{add reference to before and later... as mentioned we would run evaluations on secure prediction of different models. Here we describe scenario in detail..}

@@

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.

@@

\subsection{Comparison with Yao-only approach}
Before we provide the formalization of our compiler, we show that for performance it it critical to use a mix of arithmetic and boolean circuits.
We demonstrate the performance benefits of mixed computation over boolean-only compute by comparing with previous tools CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm} that are based on Yao's garbled circuits. As we already mentioned that we are not the first to observe that Yao-only approach does not scale well beyond examples with small numbers of multiplications \cite{aby,tasty,autos,secureml,minionn,chameleon}, especially for large-scale multiplications commonly found in Machine Learning (ML) algorithms -- the main use case of \tool. Indeed, this is one of the main drivers behind development of the specialized MPC protocols in previous works \cite{secureml,minionn,shafindss} with which we compare the performance of our automatically generated protocols in \sectionref{eval}.

The largest example benchmark in CBMC-GC is multiplication of two $8\times 8$ matrices for which it generates <FILL> gates and takes <FILL> seconds to run. In contrast, in \tool we use arithmetic sharing for this compute that generates <FILL> gates and completes in <FILL> seconds. We tried running CBMC-GC for multiplying two $20\times 20$ matrices and it timed out after 5 hours. In contrast, most of our benchmarks are much bigger. For example, we run a moderate size DNN for <FILL> in <FILL> seconds which contains a multiplication of <FILL> matrix and <FILL> matrix as a sub-computation. On the other hand, ObliVM scales to larger benchmarks with its use of Yao-pipelining \cite{yao-pipe}. We ran inner-product computations of varying lengths followed by a comparison in both ObliVM and \tool (see Table~\cite{oblivm-compare}). Our experiments show that we are atleast 30x faster than ObliVM due to our use of arithmetic sharing for inner-product computation.

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
\dg{Points to address. 1. hard problem nto solve optimally 2. some decisions are fixed and some are context sensitive 3. our heuristics and their basis}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. We analyse these costs by running microbenchmarks for basic operations and interconversions and obtained numers consistent with ABY~\cite{aby} (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean. However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use some heuristics based on costs observed using microbenchmarking. Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

>>>>

\section{\tool Overview}
\label{sec:ex}
%$w^Tx>0$, mnist logistic regression
%% \divya{add reference to before and later... as mentioned we would run evaluations on secure prediction of different models. Here we describe scenario in detail..}

@@

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays \dg{with public indices}, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.
\TODO{Add a justification for not having secret indices, public inputs etc. Unless there is a better place to have those.}

@@

\subsection{Comparison with Yao-only approach}
Before we provide the formalization of our compiler, we show that for performance it it critical to use a mix of arithmetic and boolean circuits.
We demonstrate the performance benefits of mixed computation over boolean-only compute by comparing with previous tools CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm} that are based on Yao's garbled circuits. As we already mentioned,  we are not the first to observe that Yao-only approach does not scale well beyond examples with small numbers of multiplications \cite{aby,tasty,autoS,secureml,minionn,chameleon}, especially for large-scale multiplications commonly found in Machine Learning (ML) algorithms -- the main use case of \tool.  
\dg{Speaking loosely,} multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Indeed, this is one of the main drivers behind development of various specialized MPC protocols in previous works \cite{secureml,minionn,shafindss} that we compare against in \sectionref{eval}.

The largest example benchmark in CBMC-GC is multiplication of two $8\times 8$ matrices for which it generates <FILL> gates and takes <FILL> seconds to run. In contrast, in \tool we use arithmetic sharing for this compute that generates <FILL> gates and completes in <FILL> seconds. We tried running CBMC-GC for multiplying two $20\times 20$ matrices and it timed out after 5 hours. In contrast, most of our benchmarks are much bigger. For example, we run the secure computation of a DNN for CIFAR-10 in 265 seconds which requires multiplying a $64\times576$ matrix with a $576\times1024$ matrix as a sub-computation. On the other hand, ObliVM scales to larger benchmarks with its use of Yao-pipelining \cite{yao-pipe}. We ran inner-product computations of varying lengths followed by a comparison in both ObliVM and \tool (see Table~\cite{oblivm-compare}). Our experiments show that we are atleast 30x faster than ObliVM due to our use of arithmetic sharing for inner-product computation.

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
\dg{Points to address. 1. hard problem to solve optimally 2. some decisions are fixed and some are context sensitive 3. our heuristics and their basis}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. We analyse these costs by running microbenchmarks for basic operations and interconversions and our observations were consistent with ABY~\cite{aby} (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean \dg{($\sim9x$ time $\&$ $\sim20x$ comm. in LAN setting)}.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an \dg{NP-hard} problem and in this work, we use some heuristics based on costs observed using microbenchmarking. Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

\dg{\textsc{People wanted estimate of interconversion costs. I don't know where to put it. May be implementation?} Interconversion costs: Converting from A to Y requires computing computing a Yao circuit for addition that is linear size and hence, requires linear number of symmetric key operations. Similarly, Y2A requires computing a subtraction circuit that is again linear size.}

### 2018-05-06 ccs/impl.tex
ccc
changes, comments

The compilation rules of \figureref{compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations.
For instance, if boolean shares of a variable are available in scope and the variable is involved in
an addition then \tool performs the addition in boolean rather than first coercing boolean to arithmetic
and then performing an arithmetic addition. However, multiplication is always performed in arithmetic
as the cost of a boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean~\cite{aby}.
Other optimizations include the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.

>>>>

\dg{remove addition?}
The compilation rules of \figureref{compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations.
For instance, if boolean shares of a variable are available in scope and the variable is involved in
an addition then \tool performs the addition in boolean rather than first coercing boolean to arithmetic
and then performing an arithmetic addition. 
%However, multiplication is always performed in arithmetic as the cost of a boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean~\cite{aby}.
Other optimizations include the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.

### 2018-05-06 ccs/intro.tex
changes, comments

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
\dg{It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autos,secureml,minionn,chameleon}.}
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%

>>>>

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
\dg{It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autoS,secureml,minionn,chameleon}.}
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
